Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-23 paper.tex
Updated explination of mesh parameters, including R_{sri} being independant. Fixed error mesh parameter table.

The electrical impedance between two electrodes in an electrolyte arises from two interface impedances in series with the resistance due to the bulk of the electrolyte itself. To quantify the impedance presented by a single interface we first need to understand the inter-electrode resistances presented by the electrolyte bulk. As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.
In \cite{ScottSingle2013}, a series of transresistance measurements were used in conjunction with a physical description of the electrode geometry to build up a representative network of resistors. Repeating this work, we can then produce a resistor network that connects each of the 8 electrodes, replicating the resistances due to the solution bulk. Transimpedance measurements were taken at each concentration of PBS and the results are presented in figure~\ref{fig:transresistance}.
A numerical fit was made to the two independent scaling parameters ($R_{eri}$ and $R_{sri}$).  The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.

@@

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $R_{eri}$ & 0.407 / $\sigma$ \\ \hline
            $R_{sri}$ & 3.71 / $\sigma$ \\ \hline
            $R_{li}$ & $R_{eri}$ $3/4$ \\ \hline
            Depth & 5 layers \\ \hline
            Padding & 3 layers \\ \hline
        \end{tabular}
    \end{center}
    \caption{Resistor mesh parameters. $\sigma$ measured in units of $S/cm$}
    \label{tab:RESparams}
\end{table}

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution. Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS. 
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.

@@

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    {\color{Red} Estimate current density and investigate possible effects}
    Maximum and minimum current density figures added. No comment on effect formed yet. No response yet.
}

@@

1. You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14). I want to know how much charge was being applied to these electrodes at low frequencies (e.g. 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
{\color{OliveGreen}
    Item 18\\
    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
    No response yet.
}\\

>>>>

The electrical impedance between two electrodes in an electrolyte arises from two interface impedances in series with the resistance due to the bulk of the electrolyte itself. To quantify the impedance presented by a single interface we first need to understand the inter-electrode resistances presented by the electrolyte bulk. As there are always two interface impedances between any two electrodes, inter-electrode resistances cannot be measured in isolation.

In \cite{ScottSingle2013}, a series of transresistance measurements were used in conjunction with a physical description of the electrode geometry to build up a representative network of resistors. The network in that paper was defined using five parameters: $R_{eri}$, $R_{lri}$, $R_{li}$, mesh depth, and edge depth. Readers are advised to read that paper to understand the interpretation of these model parameters. Repeating that work, a resistor network that connects each of the eight   electrodes is has been constructed, mimicking the resistances due to the solution bulk. The mesh depth and padding values of five columns and three rows, respectively, has been taken directly from \cite{ScottSingle2013}.
A numerical fit was made to the two independent scaling parameters $R_{eri}$ and $R_{li}$
\footnote{The values of $R_{eri}$ and $R_{sri}$ are defined by the lengths of the electrode and inter-electrode spacers respectively as described in \cite{ScottSingle2013}. The two parameters are proportional to each other by the ratio of their lengths. Hence, we define $R_{sri}$ to be 3/4 that of $R_{eri}$ making it a dependant parameter.}.
The resulting fit and parameter values are presented in figure~\ref{fig:transresistance} and table~\ref{tab:RESparams} respectively.

@@

\begin{table}
    \begin{center}
        \begin{tabular}{|r|l|}
            \hline
            $R_{eri}$ & 0.407 / $\sigma$ \\ \hline
            $R_{sri}$ & $R_{eri}$ $3/4$ \\ \hline
            $R_{li}$ & 3.71 / $\sigma$ \\ \hline
            Depth & 5 layers \\ \hline
            Padding & 3 layers \\ \hline
        \end{tabular}
    \end{center}
    \caption{Resistor mesh parameters. $\sigma$ measured in units of $S/cm$}
    \label{tab:RESparams}
\end{table}

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution. Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS. The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point.
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.

@@

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    {\color{Red} Estimate current density and investigate possible effects}
    Maximum and minimum current density during displacement current measurement added. No comment on effect formed yet. No response yet.
}

@@

1. You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14). I want to know how much charge was being applied to these electrodes at low frequencies (e.g. 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
{\color{OliveGreen}
    Item 18\\
    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
    Added current density and peak stimulus voltage information to displacement current measurement. Still needs total charge transfer for both CPE and Faradaic.
}\\
